---
title: "Prediction Assignment Writeup"
author: "GM"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Read and clean the data. Columns are either almost all NA or never NA. I drop the columns that are primarily NA and ones that do not seem relevant to the classes. I do not split the train set into two since I will use cross validation.

```{r data}
set.seed(888)
train <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv')
test <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv')
train <- train[,colSums(is.na(train))==0]
rm_vars <- grepl("^X|time|window", names(train))
train <- train[,!rm_vars]
```

```{r more_cleaning}
nzv <- nearZeroVar(train)
train <- train[,-nzv]
```

I created a random forest to predict the classes. Random forest is an ideal algorithm for cross validation and class predictions. 



```{r model}
controlRF <- trainControl(method='cv', 3)
modelRF <- train(classe~., data = train,
                 , trControl = controlRF, method = 'rf')
```
I expect about 99% accuracy. The model is likely to be wrong about 1% of the time.
```{r model_evaluation}
modelrf
```

```{r results_for_quiz}
predict(modelRF, newdata = test)


```

